ggplot and the venn diagram for the lefse bars !

### 2020-12-19 scripts/40_combine_all_samp_pheno.Rmd
update

>>>>

```{r}
tally <- ALL %>% 
  select(center, outcome) %>% 
  mutate_if(is.factor, as.character) %>% 
  gather('metric', 'value', cr_d100 : crs)

individual <- tally %>% 
  count(center, metric, value) %>% 
  filter(value != 'not_assessed') %>% 
  spread('metric', 'n', fill = 0)

pull_ <- tally %>% 
  count(metric, value)  %>% 
  filter(value != 'not_assessed') %>% 
  mutate(center = 'pull') %>% 
  spread('metric', 'n', fill = 0) %>% 
  select(colnames(individual))

tally_all <- bind_rows(
  individual, pull_
)

```

```{r}
library(kableExtra)

kbl(tally_all, caption = "") %>%
  kable_minimal( full_width = F) %>%
  pack_rows("Group Italy", 1, 2) %>%
  pack_rows("Group MSK", 3, 4) %>% 
  pack_rows("Group UPENN", 5, 6)  %>% 
  pack_rows("Group ALL", 7, 8)

```

### 2020-12-19 scripts/43_comparisons_3.Rmd
update

```{r}
fullgenefam <- read_tsv('../data/shotgun_output/humann3_tsv/humann3_genefamilies_CART.tsv')  %>% 
  rename_all(funs(str_replace(., '^CART_','')))  %>% 
  rename_all(funs(str_replace(., '_humann3$','')))

gfcts <- sub_phenos %>% 
  map(~ pull(.data = ., fid) ) %>% 
  imap(~ fullgenefam %>% select(`# Gene Family`, matches(.x)) %>% 
         write_tsv(str_glue('../data/shotgun_output/humann3/{.y}_gfcts.tsv'))) 
```

@@

all_pcts <- all_sub_pheno %>% 
  map(~ pull(.data = ., fid) ) %>% 
  imap(~ full %>% select(`# Pathway`, matches(.x)) %>% 
         write_tsv(str_glue('../data/shotgun_output/humann3/pull_{.y}_pcts.tsv')))
```

@@

cmds <- tibble(
  fns = fns
) %>% 
  mutate(format_cmd = str_glue('format_input.py {fns}  {fns}.in -c 1 -u 2 -o 1000000')) %>% 
  mutate(run_cmd = str_glue('run_lefse.py {fns}.in  {fns}.res')) %>% 
  mutate(plot_cmd = str_glue('plot_res.py {fns}.res {fns}.png  --feature_font_size 4 --width 10 --dpi 300')) %>% 
  select(-fns) %>% 
  gather() %>% 
  select(value) %>% 
  write_csv('../data/shotgun_output/humann3/lefse_run_cmd.sh', col_names = F)
```

@@

cmds <- tibble(
  fns = fns
) %>% 
  mutate(format_cmd = str_glue('format_input.py {fns}  {fns}.in -c 1 -u 2 -o 1000000')) %>% 
  mutate(run_cmd = str_glue('run_lefse.py {fns}.in  {fns}.res')) %>% 
  mutate(plot_cmd = str_glue('plot_res.py {fns}.res {fns}.png  --feature_font_size 4 --width 10 --dpi 300')) %>% 
  mutate(clado_cmd = str_glue('plot_cladogram.py {fns}.res {fns}_clado.png  --label_font_size 4 --dpi 300 --format png --title {fns}')) %>% 
  select(-fns) %>% 
  gather() %>% 
  select(value) %>% 
  write_csv('../data/shotgun_output/humann3/lefse_run_cmd_taxa.sh', col_names = F)
```

>>>>

```{bash}
# regroup the whole gene family table here
humann_regroup_table --input humann3_genefamilies_CART.tsv --groups uniref90_ko --output humann3_KO_CART.tsv
```

```{r}
fullko <- read_tsv('../data/shotgun_output/humann3_tsv/humann3_KO_CART.tsv')  %>% 
  rename_all(funs(str_replace(., '^CART_','')))  %>% 
  rename_all(funs(str_replace(., '_humann3$','')))

kocts <- sub_phenos %>% 
  map(~ pull(.data = ., fid) ) %>% 
  imap(~ fullko %>% select(`# Gene Family`, matches(.x)) %>% 
         write_tsv(str_glue('../data/shotgun_output/humann3/{.y}_kocts.tsv'))) 
```

```{r}
# the lefse for the ko only
fns <- list.files('../data/shotgun_output/humann3/', pattern = 'lefse_ready_kocts.tsv$')

cmds <- tibble(
  fns = fns
) %>% 
  mutate(format_cmd = str_glue('format_input.py {fns}  {fns}.in -c 1 -u 2 -o 1000000')) %>% 
  mutate(run_cmd = str_glue('run_lefse.py {fns}.in  {fns}.res')) %>% 
  mutate(plot_cmd = str_glue('plot_res.py {fns}.res {fns}.png  --feature_font_size 4 --width 10 --dpi 300 --title {fns}')) %>% 
  select(-fns) %>% 
  gather() %>% 
  select(value) %>% 
  write_csv('../data/shotgun_output/humann3/lefse_run_cmd_KO.sh', col_names = F)
```

@@

all_pcts <- all_sub_pheno %>% 
  map(~ pull(.data = ., fid) ) %>% 
  imap(~ full %>% select(`# Pathway`, matches(.x)) %>% 
         write_tsv(str_glue('../data/shotgun_output/humann3/pull_{.y}_pcts.tsv')))

all_kocts <- all_sub_pheno %>% 
  map(~ pull(.data = ., fid) ) %>% 
  imap(~ fullko %>% select(`# Gene Family`, matches(.x)) %>% 
         write_tsv(str_glue('../data/shotgun_output/humann3/pull_{.y}_kocts.tsv')))
```

@@

cmds <- tibble(
  fns = fns
) %>% 
  mutate(format_cmd = str_glue('format_input.py {fns}  {fns}.in -c 1 -u 2 -o 1000000')) %>% 
  mutate(run_cmd = str_glue('run_lefse.py {fns}.in  {fns}.res')) %>% 
  mutate(plot_cmd = str_glue('plot_res.py {fns}.res {fns}.png  --feature_font_size 4 --width 10 --dpi 300 --title {fns}')) %>% 
  select(-fns) %>% 
  gather() %>% 
  select(value) %>% 
  write_csv('../data/shotgun_output/humann3/lefse_run_cmd.sh', col_names = F)
```

@@

cmds <- tibble(
  fns = fns
) %>% 
  mutate(format_cmd = str_glue('format_input.py {fns}  {fns}.in -c 1 -u 2 -o 1000000')) %>% 
  mutate(run_cmd = str_glue('run_lefse.py {fns}.in  {fns}.res')) %>% 
  mutate(plot_cmd = str_glue('plot_res.py {fns}.res {fns}.png  --feature_font_size 4 --width 10 --dpi 300 --title {fns}')) %>% 
  mutate(clado_cmd = str_glue('plot_cladogram.py {fns}.res {fns}_clado.png  --label_font_size 4 --dpi 300 --format png --title {fns}')) %>% 
  select(-fns) %>% 
  gather() %>% 
  select(value) %>% 
  write_csv('../data/shotgun_output/humann3/lefse_run_cmd_taxa.sh', col_names = F)
```

### 2020-12-19 scripts/44_ggplot_venn_lefse.Rmd
update

@@

res_all_list <- res_all %>% 
  split(.$tbl) %>% 
  map(~split(., list(.$cohort, .$outcome )) %>% 
  map(~ pull(.data = ., feature)) %>% 
  compact())

vars <- res_all %>% 
  distinct(outcome) %>% 
  pull(outcome)

@@

>>>>

## collect all of the res files

@@

res_all_list <- res_all %>% 
  split(.$tbl) %>% 
  map(~split(., list(.$cohort, .$outcome )) %>% 
  map(~ pull(.data = ., feature)) %>% 
  compact())
```

```{r}
vars <- res_all %>% 
  distinct(outcome) %>% 
  pull(outcome)

@@

## a PCOA to see how the data

```{r}
cts <- read_tsv('../data/shotgun_output/humann3/') %>% 
  gather('sampleid', 'value', names(.)[2]:names(.)[ncol(.)]) %>% 
  rename(pathway =  names(.)[1]) %>% 
  spread('pathway', 'value') %>% 
  column_to_rownames('sampleid')
dist_bl <- vegan::vegdist(cts, method = 'bray')
bl_bc <- cmdscale(dist_bl, k = 2) 
pheno <- read_csv('../data/shotgun_pheno/final_comprehensive.csv') %>% 
  mutate(sampleid = fid)
bl_bc %>% 
    as.data.frame() %>% 
    rownames_to_column('sampleid') %>% 
    inner_join(pheno, by = 'sampleid') %>% 
    ggpubr::ggscatter(x = 'V1', y = 'V2', color =  'center',  shape = 'toxicity') 
```
